Malacology: A Programmable Storage System

### 2016-10-20 paper/paper.tex
wordsmithing

We wanted to implement CORFU and we had two choices: build it from the ground
up or do it on top of Malacology. To show the feasability of building on
Malacology our evaluation focuses on the performance of the internal
abstractions used to construct the Mantle and ZLog services. We also discuss
latent capabilities we discovered in this process that lets us navigate
different trade-offs within the services themselves. First, we benchmark
scenarios where contention is at the sequencer by examining the interfaces used
to map ZLog onto Malacology; specifically, we describe the sequencer
implementation and the propagation of object \& data interfaces interfaces.
Next, we benchmark scenarios when there are multiple logs by using Mantle to
balance sequencers across a cluster.

Detailed system-wide performance measurements and analysis is forthcoming for
both Mantle and ZLog, as we try to find the best metadata balancing policies
and physical design implementation trade-offs.  Since this work
focuses on the programmabilty of Malacology, the goal of the benchmarks is to
show that the components and subsystems that support the Malacology interfaces
provide reasonable performance.

\subsection{Mapping ZLog onto Malacology}
\label{sec:mapping-zlog-onto-malacology}
We evaluate the mapping of ZLog onto Malacology by examining the costs of
utilizing the metadata service as a sequencer, and propagating interface
changes throughout the cluster using the monitoring service. We have omitted
evaluation of the overhead costs of adding object interfaces themselves due to
lack of space, and the fact that they are heavily tested and used already in
production with acceptable performance, introducing a small constant overhead
per operation but otherwise does not affect scalability.

@@

\begin{figure}[h]
\centering
\includegraphics{figures/caps-delay-thruput.png}
\caption{[\href{https://github.com/double-blind-submitter/osdi16}{source}]
Sequencer throughput by re-using various services.  The highest performance is
achieved using a single client with exclusive, cacheable privilege. Round-robin
sharing of the sequencer resource is affected by the amount of time the
resource is held, with best-effort performing the worst.}
\label{fig:captp}
\end{figure}

>>>>

%We wanted to implement CORFU and we had two choices: build it from the ground
%up or do it on top of Malacology. To show the feasability of building on
%Malacology our evaluation focuses on the

Our evaluation demonstrates the feasibility of building new service abstractions
atop programmable storage, focusing on the
performance of the internal
abstractions exposed by Malacology and
used to construct the Mantle and ZLog services. We also discuss
latent capabilities we discovered in this process that let us navigate
different trade-offs within the services themselves. First, we benchmark
scenarios 
%where contention is at the sequencer 
with high sequencer contention
by examining the interfaces used
to map ZLog onto Malacology; specifically, we describe the sequencer
implementation and the propagation of object and data interfaces interfaces.
Next, we benchmark scenarios in which the storage system manages multiple logs by using Mantle to
balance sequencers across a cluster.

% should save this for future work, otherwise it undercuts the eval.
%Detailed system-wide performance measurements and analysis is forthcoming for
%both Mantle and ZLog, as we try to find the best metadata balancing policies
%and physical design implementation trade-offs.

Since this work
focuses on the programmabilty of Malacology, the goal of the benchmarks is to
show that the components and subsystems that support the Malacology interfaces
provide reasonable performance, as well as to give examples of the flexibility
that Malacology provides to programmers.
%As we search for the best metadata balancing policies
%and physical design implementation trade-offs,
%we plan to rel

\subsection{Mapping ZLog onto Malacology}
\label{sec:mapping-zlog-onto-malacology}
We evaluate the mapping of ZLog onto Malacology by examining the costs of
utilizing the metadata service as a sequencer, and of propagating interface
changes throughout the cluster using the monitoring service. We have omitted
evaluation of the overhead costs of adding object interfaces themselves due to
lack of space, and the fact that they are heavily tested and used already in
production with acceptable performance, introducing a small constant overhead
per operation without affecting scalability.

@@

\begin{figure}[h]
\centering
\includegraphics{figures/tradeoff.png}
\caption{[\href{https://github.com/double-blind-submitter/osdi16}{source}]
Sequencer throughput by re-using various services.  The highest performance is
achieved using a single client with exclusive, cacheable privilege. Round-robin
sharing of the sequencer resource is affected by the amount of time the
resource is held, with best-effort performing the worst.}
\label{fig:captp}
\end{figure}
